### 2020-04-24 MS-A4-2_Types_of_Relationships.rmd
Initial commit

---
title: "MS-4.2 Types of Relationships"
output:
  html_document:
    code_folding: "hide"
header-includes:
- \ifdefined\HCode\def\pgfsysdriver{pgfsys-dvisvgm4ht.def}\fi
- \usepackage{tikz}
---

# [Syllabus](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf) {.tabset .tabset-fade .tabset-pills}

## Show

::: {.syllabus}

Students:

* use an exponential model to solve problems
  + graph and recognise an exponential function in the form $y=a^x$ and $y=a^{-x} (a>0)$ using technology
  + interpret the meaning of the intercepts of an exponential graph in a variety of contexts
  + construct and analyse an exponential model to solve a practical growth or decay problem
* construct and analyse a quadratic model to solve practical problems involving quadratic functions of expressions of the form $y=ax^2+bx+c$, for example, braking distance against speed
  + recognise the shape of a parabola and that it always has a turning point and an axis of symmetry
  + graph a quadratic function using technology
  + interpret the turning point and intercepts of a parabola in a practical context
  + consider the range of values for $x$ and $y$ for which the quadratic model makes sense in ap ractical context
* recognise that reciprocal functions of the form $y=\frac{k}{x}$, where $k$ is a constant, represent inverse variation, identify the rectangular hyperbolic shape of these graphs and their important features
  + use a reciprocal model to solve practical inverse variation problems algebraically and graphically, eg the amount of pizza received when sharing a pizza between increasing numbers of people
:::

## Hide

#  {.tabset .tabset-fade .tabset-pills}

## Exponentials {.tabset .tabset-fade .tabset-pills}

### Functions

<div id="exp1"></div>

<script>
var exp1 = {
"id": "exp1",
"width":1406,
"height":718,
"showMenuBar":true,
"showAlgebraInput":true,
"showToolBar":true,
"customToolBar":"0 77 73 62 | 1 501 67 , 5 19 , 72 75 76 | 2 15 45 , 18 65 , 7 37 | 4 3 8 9 , 13 44 , 58 , 47 | 16 51 64 , 70 | 10 34 53 11 , 24  20 22 , 21 23 | 55 56 57 , 12 | 36 46 , 38 49  50 , 71  14  68 | 30 29 54 32 31 33 | 25 17 26 60 52 61 | 40 41 42 , 27 28 35 , 6",
"showToolBarHelp":true,
"showResetIcon":false,
"enableLabelDrags":false,
"enableShiftDragZoom":true,
"enableRightClick":false,
"errorDialogsActive":false,
"useBrowserForJS":false,
"allowStyleBar":false,
"preventFocus":false,
"showZoomButtons":true,
"capturingThreshold":3,
// add code here to run when the applet starts
"appletOnLoad":function(api){ /* api.evalCommand('Segment((1,2),(3,4))');*/ },
"showFullscreenButton":true,
"scale":1,
"disableAutoScale":false,
"allowUpscale":false,
"clickToLoad":false,
"appName":"graphing",
"showSuggestionButtons":true,
"buttonRounding":0.7,
"buttonShadows":false,
"language":"en",
// use this instead of ggbBase64 to load a material from geogebra.org
// "material_id":"RHYH3UQ8",
// use this instead of ggbBase64 to load a .ggb file
// "filename":"myfile.ggb",
"ggbBase64":"UEsDBBQACAgIAFFgl1AAAAAAAAAAAAAAAAAXAAAAZ2VvZ2VicmFfZGVmYXVsdHMyZC54bWztml1T4zYUhq+7v0Kjq/aCxHZiEhjMDrsznTLDskxhdnqr2CeOiiO5kkwcfv3KkmM7EKchZJuwhQuU4+jDet6joyM7Zx/zaYIeQEjKWYDdjoMRsJBHlMUBztT4aIg/nn84i4HHMBIEjbmYEhVgv6hZtdNWxx8Mi2skTQMcC5JOdBcYpQlRRZsAzzBCuaSnjF+TKciUhHAbTmBKrnhIlOlmolR62u3OZrPOYsAOF3FX9ym7uYy6caw6usRI3zWTAS4/nOp+l1rPeqad5zhu968vV3acI8qkIiwEjPSMIhiTLFFSf4QEpsAUUvMUApxyyhRGCRlBEuCbwkK/jgXAbxiVjTQoB59/+OVMTvgM8dHfEOprSmRQtTNGt6ijv/7MEy6QCLDnYhQXrXU50uWJp4El6YQE2LG1EzIHgR5IUl0hmeKh6cBcHZNEwqKuHuoLj8B+0y/rMzo1PJFUoLVwOnowmQJEekBcTtI1ysyNyo0eQ85FJFEe4GtyjdG8LB9taaoYPLf0sRzUb15V8wQa937WLcluxjiCFFikKy2BdrcCfTIwoItiZIt3zGsxH79jbsfsvpzzV9ak672ZaPEmnPiS/Qmxvucm4t474l0iXvbf/v8TrqliMcrif4BDPk0TyHfIPqGs5nhljIq7t12W4RjsjoHu7CkkO1tDL4BYfGpCw3sGUhZs636LD3/QSG9hZjyuM0mqdE/uYGh7gH/YkmiZBLFehHHGQmUCSgn2cyYemkr0+s4+tKj73Nr7W4TYmrLn9NezlBAXVsXldmHXbr1dTvfu1qvdWlPKVFLc0yVT+kQGxpXls2nfA6R3epCv7E4QJotT2bKXtWsqyHydnv5b0PNdzafR7vobEZVGmT4TjPWsoqaw2yVVTWE936+l7Xj+vtV9wR6wksh2mdDBuvoL/Xg3bnW8Xbwodp6VGDuDA3arBz09XvP4Vpp1ZvEmcrwDC54rEnMiFEhK2L+ddJJ53FjjNwu70mNg9XhtfrTb01LHdeyf2z9xXPfY9fYt9HrES4eam+pCDdl9HeTKEQ582WyeQ7bzDDmjYX0wsVZFsv+ThY8dJFY0BmajrkQod0y1uWMaPzrlO47cNfbcNd8+uvayaa9vXNAcXdgWF7bihWeLni36tvArQC8/chpZUx21Gon1k62hv9056W0Fkl2E2oOS/D9I4Fk2BdEICtcLu3Id34YF3V8GS7JuEATafKTdI2RCI+0+U6oFOtLKTUluFCQjyZNMwW0oAFj9ns868YxGalKoqMce07xwFdsnmnBBHzlTFQ1UrIGLxLwRXHoqssp1vHXp65Kjvi4wExYn9Vq8sFatgH3mbyo9fRq4SpgmQ6dEeNzxhj136PecgTs48YfHGyJ1hzVS+8XGRH+If7xohXvNoO73yr5FWD9o7Tk7VvLZ0e/36kJ9aDnE539G42dVf9ijvYSHmawfVlurIjT8yVIRkuU0oUTMX+fPK5KUdsIK8johuDNG4zcHBwi4fSoae1zf2qW1Gu/17WTGVFNkZKob2EEo+0TC+1jwjEXPN5qdTN3dt2+1QxtxngCpA9Gnhd14l/xsa28DVO6m+1x94QTC+xHPl3aj9TGGynoFXBmj8ZJ3xQrYfJbFAlqe59HeXWGbR3Btbx5X5hpN0t3Gj566i19YnX8HUEsHCGqraC7bBAAABCYAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAAFwAAAGdlb2dlYnJhX2RlZmF1bHRzM2QueG1s7ZjdbtMwFMev4Sks39PYaZIu0zJUwQVIMIF2w62XnLaGxA62uzZ7Nd6BZ+LEzroUNsSqbRKIXPT46xzHv79zEvfk5bapySUYK7UqKJ8wSkCVupJqWdC1W7w4oi9Pn58sQS/hwgiy0KYRrqBpP3Lnh7VJOjvq20TbFnRpRLvCEJS0tXC9T0E3lJCtlcdKn4kGbCtKOC9X0Ih3uhTOh1k51x5H0WazmVxPONFmGWFMG21tFS2XboKWErxrZQs6FI4x7p73Zur9YsZ49On9uzDPC6msE6oESnBFFSzEunYWi1BDA8oR17VQ0FIrWU5xjlpcQF3Qt8rhMqHsb5GUa3OJ/oNzQac8ZfT0+bMTu9Iboi8+47iCOrOGnb+vRP0Y7H6la22IKWjMKUHCnKG9QJvHiK5uV6KgbMJZuHiSM84zHgf/WnRgyKXAoCy0iLXTpQ/pWxeitnA9Fid/rysIPckwXsnGsybWAeqEk9sWoPKlsHzmNeu8/uN4UsG562ogbiXLLwos4k9HTn3hjawq6LdR8AG5BHWJRLSxqD3zs3TMD79iw27bcl/vuO+94qHZ++OtGrkl8+AxDwPncTDTYJJg0h0S+KrCfdr+F/ewBdP3nESDzL8ILrbSjvSe99XXexqz6UEaMy8x8wKzG3kfS0zcN48r509kW2HwQUaJSpwjlAFX/f3b73H7R6gUxoGVQo3Av+o7fiaf/Q3kH5P73SAxvoIRvw++vscPE+BB/PLcA4x57hF6u8tO6UNhLLU2lSXbgp6JM0wBg70a7CZYP3Qh+jfSMNud+fE2uOxAuLruVlAZrW74jppuEE8HxIc8UQ/60kgGKGmesSRLHkylQzf7vdjOTbmSDVQg9uGitE8HN9BNZh5ub/4Nth86zM2y2uf6lJs2JJM8cI3ZP8PVSNvsU+VPSDULKTpQzbO/kqoCt1vnWV8e59X0f169H82va1H5r7FhsR+v62Oq/MDjyt3JMUvy/pplPD3iScwfCtBjHDluPXD0jeFU0QVzFe8C3vcMQuZZMLNgjoLJ7zyfyKatZSnd76W1a7PAA/Ntn81D177KyWEqo9+tH86T2Z9u+5vAT3Ro4X/6fReNTvzR9d8Lpz8AUEsHCBnmYOpCAwAAAREAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAAFgAAAGdlb2dlYnJhX2phdmFzY3JpcHQuanNLK81LLsnMz1NIT0/yz/PMyyzR0FSorgUAUEsHCNY3vbkZAAAAFwAAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAADAAAAGdlb2dlYnJhLnhtbL1YW2/bNhR+bn/FgZ42IIlJSpTkwu6QpBs2oO2KZRuGPQygJdrmIkuCRMdO0R+/c0hJlnMpmqZYGpUieXgu37lRmf2w3xRwo5vWVOU84GcsAF1mVW7K1TzY2uVpGvzw+uVspauVXjQKllWzUXYeSKIczuHsTCYpram6ngerRtVrZBFAXShLZ+bBLgCTz4M3l2nEfpLhqWTTi9PoMr08PX8j35zKVFywy+TyR8HiAGDfmldl9V5tdFurTF9la71Rb6tMWSdwbW39ajLZ7XZnvWpnVbOaoPR2sm/zyWq1OMMxALSvbOdB9/IK+R6d3oXunGCMT/5699bLOTVla1WZ6QDI9q15/fLFbGfKvNrBzuR2jUhFpOZam9Ua0Uh4GsCEqGqEpNaZNTe6xbOjqbPeburAkamS9l/4NygGwwLIzY3JdTMP2BkLp6mYhkxM04RPk0QEUDVGl7Yj5p3QSc9udmP0zvOlNycyYtMEXWVasyj0PFiqokW7TLlsENxh3trbQi8UirXNFucHjfiJ+4ck5qMmduhkjwXuMXZCT4KPlMyrM5ItOapsq6pwnBl8Ag6S4QN8CicQJ7gigEuIcCXFlQRCWpM8ghCIhIcQRThGtMxj3KFt/B/FAee4A4KBECA4iBCnUoJEsoTOCqSNp44fw4eoUSN8QloLQ3zcWhjhI+gNGUnPBvWQYezeJFEjfynIArcYphBNURAtyIRDiDrgPGGAHENiz50dEQP65RARe5GASAH5oenEmYmnOKZbuOOZ3i/yIb/E+DiH3fFLdOwVdAJD205o4H4QfpX5KQv9IPwQ+UF6msifjDypN5RFniYKn2thb1/4FPvSkX2cjEB/kPZuCIH05k5/GqJuGvupCzTGWbea+tUpTeNnGhN+lTF8JNUn51OE9iJ5KJ8g83mBebAzfYqdz4T3QXAlFib6dc89keGT7LxXGb9CYnyUet/G4Cj9YvFcpP+7zIQ9WG38yLvx2zhi+uWOeG5lGoCQnxc5m/Q9edaBAO2aaLtUtnrTEixJAkkIsRh6ZEwtrGuUiYBEQhKP2uUJNcxYHnomdcz0qGfK9LhxxrSYuC6MfYp6nu+gIuqb6EnXRj/da6PY9aJD40MFiRUHwEYNMdXIrgOiFmLogUJSGxQxYJ+UAmKqw4+0Q7wpVq0ZsF3roh5QdzCast7aI+iyTd6/2gqpVeHugR19XmXXFwPYHSetWjtmizenwwXN36SO7m8vZoVa6AJvslcUCgA3qiD9nIRlVVroq2scOHburjjT26wwuVHln+j6/lr2frtZ6AbcazUwoeMwXCpdjR5fKh1NVlVNfnXbYqjA/m/d4Ok4kQHcdu+C6m2mKJCj6dl0/IM3v9tHttLYc9c3V9paNLEFtddtD+mqoSzpoKLJL+1FVRyW6sqU9lLVdtu4bwXUoSG9z8tVoR1azpF4n86uF9X+ysEkYs/r99saZ6cdBovVZVVUDWCeCYl2rbpx4UdHQ6oNVMzRMEfB/D5xHfb5VDgKNy786KjQk163zlTe28l6KaYFPz8KNRcFdDnflsa+7SfWZNcHS4ne+7jH8Jgl/xYsuyy50efI9iBmNrkTcrO2brTK27XWtg/Co1AbxVlnOx5YXuqiuBqTJffpWl1QflQlwPoqa6qi8I1s9J5VxXZTOgdDQyZ7T88m97SadUnb67ipcu2TLPQnjvZn17opdeFzosSY3Vbb1pP7qHQKblv9Qdn1eZn/pleo5wdFRd0iiJ704JtcZ2aDB7u0DjuPUQT/gV7xy7leNbp3ptfGh1CnJoyMGkDyKXsg67GzqsEMQaEOwCN1ZpPeuplV2JVcp9oYghGjeKP27laGRaDuiseszRpTU+bCAhvTtT4kZ25aYpGPcCHEWpTlXWeNpRjDz/WtXVeN++5UllaofBV6gx+ZYF2WltuNbkw2RKxyH7Co+ra37Yx3SUrxCtXiX4yPO2F+wBy3H8ljUEW9Vo4f8z88mjLOY95nr7qlAjrC03F/N8RMX1ML+oD22LEOOvSTWrQYl1ZjoGpdHv6W4BXtAl5Q30b6GIdb/JDAc0uzH0GLaJmPGHyD61yWnvvAGBt6qDV2jVmNH+hUcOgu5GDtXn42ea7LQXU1xAZ2Ie2rxkBfIwCu1o7S3ruKnLbHMGzpzzE95kvsd3vqot/tv4c5qH9w9F3v2MHLbemCIjgc/Lwz+2Z6Qx+S95waxb72Cl/B5cixn3Xjr8tlqy1hLzz2p2L6oJe7aHBuuZvRD4IuH8Ucqlplxt6SzOguopNxxrjm3v2l6fV/UEsHCJxE9uqtBgAANhMAAFBLAQIUABQACAgIAFFgl1Bqq2gu2wQAAAQmAAAXAAAAAAAAAAAAAAAAAAAAAABnZW9nZWJyYV9kZWZhdWx0czJkLnhtbFBLAQIUABQACAgIAFFgl1AZ5mDqQgMAAAERAAAXAAAAAAAAAAAAAAAAACAFAABnZW9nZWJyYV9kZWZhdWx0czNkLnhtbFBLAQIUABQACAgIAFFgl1DWN725GQAAABcAAAAWAAAAAAAAAAAAAAAAAKcIAABnZW9nZWJyYV9qYXZhc2NyaXB0LmpzUEsBAhQAFAAICAgAUWCXUJxE9uqtBgAANhMAAAwAAAAAAAAAAAAAAAAABAkAAGdlb2dlYnJhLnhtbFBLBQYAAAAABAAEAAgBAADrDwAAAAA=",
};
// is3D=is 3D applet using 3D view, AV=Algebra View, SV=Spreadsheet View, CV=CAS View, EV2=Graphics View 2, CP=Construction Protocol, PC=Probability Calculator DA=Data Analysis, FI=Function Inspector, macro=Macros
var views = {'is3D': 0,'AV': 1,'SV': 0,'CV': 0,'EV2': 0,'CP': 0,'PC': 0,'DA': 0,'FI': 0,'macro': 0};
var applet = new GGBApplet(exp1, '5.0', views);
window.onload = function() {applet.inject('exp1')};
applet.setPreviewImage('data:image/gif;base64,R0lGODlhAQABAAAAADs=','https://www.geogebra.org/images/GeoGebra_loading.png','https://www.geogebra.org/images/applet_play.png');
</script>

### Modelling

## Quadratics {.tabset .tabset-fade .tabset-pills}

### Functions

### Modelling

## Reciprocals {.tabset .tabset-fade .tabset-pills}

### Functions

### Modelling

## Inverse variation

## Miscellaneous problems

### 2020-04-24 MS-S5_The_Normal_Distribution.rmd
Initial commit

---
title: "MS-S5 The Normal Distribution"
output:
  html_document
---

# [Syllabus](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf) {.tabset .tabset-fade .tabset-pills}

## Show

::: {.syllabus}

Students:

* recognise a random variable that is normally distributed, justifying their reasoning, and draw an appropriate 'bell-shaped' frequency distribution curve to represent it
  + identify that the mean and median are approximately equal for data arising from a random variable that is normally distributed
* calculate the $z$-score (standardised score) corresponding to a particular value in a dataset
  + use the formula $z=\frac{x-\bar{x}}{s}$, where $\bar{x}$ is the mean and $s$ is the standard deviation 
  + describe the $z$-score as the number of standard deviations a value lies above or below the mean
  + recognise that the set of $z$-scores for data arising from a random variable that is normally distributed has a mean of 0 and standard deviation of 1
* use calculated $z$-scores to compare scores from different datasets, for example comparingnstudents’ subject examination scores
* use collected data to illustrate that, for normally distributed random variables, approximately 68% of data will have $z$-scores between -1 and 1, approximately 95% of data will have$ $z$-scores between -2 and 2 and approximately 99.7% of data will have $z$-scores between -3 and 3 (known as the empirical rule)
  + apply the empirical rule to a variety of problems
  + indicate by shading where results sit within the normal distribution, eg where the top 10% of data lies
* use $z$-scores to identify probabilities of events less or more extreme than a given event
* use $z$-scores to make judgements related to outcomes of a given event or sets of data

:::

## Hide

#  {.tabset .tabset-fade .tabset-pills}

## Normal distributions

## Properties

## $z$-scores

## Converting scrores

## Comparing datasets

## Applications

### 2020-04-24 _build.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+
+set -ev
+
+Rscript -e "rmarkdown::render()"

### 2020-04-25 ms-a4-2_non-linear-relationships.rmd
Added additional resources pages

--- 2020-04-24 MS-A4-2_Types_of_Relationships.rmd
@@
     code_folding: "hide"
-header-includes:
-- \ifdefined\HCode\def\pgfsysdriver{pgfsys-dvisvgm4ht.def}\fi
-- \usepackage{tikz}
 ---
@@
 
-<div id="exp1"></div>
-
-<script>
-var exp1 = {
-"id": "exp1",
-"width":1406,
-"height":718,
-"showMenuBar":true,
-"showAlgebraInput":true,
-"showToolBar":true,
-"customToolBar":"0 77 73 62 | 1 501 67 , 5 19 , 72 75 76 | 2 15 45 , 18 65 , 7 37 | 4 3 8 9 , 13 44 , 58 , 47 | 16 51 64 , 70 | 10 34 53 11 , 24  20 22 , 21 23 | 55 56 57 , 12 | 36 46 , 38 49  50 , 71  14  68 | 30 29 54 32 31 33 | 25 17 26 60 52 61 | 40 41 42 , 27 28 35 , 6",
-"showToolBarHelp":true,
-"showResetIcon":false,
-"enableLabelDrags":false,
-"enableShiftDragZoom":true,
-"enableRightClick":false,
-"errorDialogsActive":false,
-"useBrowserForJS":false,
-"allowStyleBar":false,
-"preventFocus":false,
-"showZoomButtons":true,
-"capturingThreshold":3,
-// add code here to run when the applet starts
-"appletOnLoad":function(api){ /* api.evalCommand('Segment((1,2),(3,4))');*/ },
-"showFullscreenButton":true,
-"scale":1,
-"disableAutoScale":false,
-"allowUpscale":false,
-"clickToLoad":false,
-"appName":"graphing",
-"showSuggestionButtons":true,
-"buttonRounding":0.7,
-"buttonShadows":false,
-"language":"en",
-// use this instead of ggbBase64 to load a material from geogebra.org
-// "material_id":"RHYH3UQ8",
-// use this instead of ggbBase64 to load a .ggb file
-// "filename":"myfile.ggb",
-"ggbBase64":"UEsDBBQACAgIAFFgl1AAAAAAAAAAAAAAAAAXAAAAZ2VvZ2VicmFfZGVmYXVsdHMyZC54bWztml1T4zYUhq+7v0Kjq/aCxHZiEhjMDrsznTLDskxhdnqr2CeOiiO5kkwcfv3KkmM7EKchZJuwhQuU4+jDet6joyM7Zx/zaYIeQEjKWYDdjoMRsJBHlMUBztT4aIg/nn84i4HHMBIEjbmYEhVgv6hZtdNWxx8Mi2skTQMcC5JOdBcYpQlRRZsAzzBCuaSnjF+TKciUhHAbTmBKrnhIlOlmolR62u3OZrPOYsAOF3FX9ym7uYy6caw6usRI3zWTAS4/nOp+l1rPeqad5zhu968vV3acI8qkIiwEjPSMIhiTLFFSf4QEpsAUUvMUApxyyhRGCRlBEuCbwkK/jgXAbxiVjTQoB59/+OVMTvgM8dHfEOprSmRQtTNGt6ijv/7MEy6QCLDnYhQXrXU50uWJp4El6YQE2LG1EzIHgR5IUl0hmeKh6cBcHZNEwqKuHuoLj8B+0y/rMzo1PJFUoLVwOnowmQJEekBcTtI1ysyNyo0eQ85FJFEe4GtyjdG8LB9taaoYPLf0sRzUb15V8wQa937WLcluxjiCFFikKy2BdrcCfTIwoItiZIt3zGsxH79jbsfsvpzzV9ak672ZaPEmnPiS/Qmxvucm4t474l0iXvbf/v8TrqliMcrif4BDPk0TyHfIPqGs5nhljIq7t12W4RjsjoHu7CkkO1tDL4BYfGpCw3sGUhZs636LD3/QSG9hZjyuM0mqdE/uYGh7gH/YkmiZBLFehHHGQmUCSgn2cyYemkr0+s4+tKj73Nr7W4TYmrLn9NezlBAXVsXldmHXbr1dTvfu1qvdWlPKVFLc0yVT+kQGxpXls2nfA6R3epCv7E4QJotT2bKXtWsqyHydnv5b0PNdzafR7vobEZVGmT4TjPWsoqaw2yVVTWE936+l7Xj+vtV9wR6wksh2mdDBuvoL/Xg3bnW8Xbwodp6VGDuDA3arBz09XvP4Vpp1ZvEmcrwDC54rEnMiFEhK2L+ddJJ53FjjNwu70mNg9XhtfrTb01LHdeyf2z9xXPfY9fYt9HrES4eam+pCDdl9HeTKEQ582WyeQ7bzDDmjYX0wsVZFsv+ThY8dJFY0BmajrkQod0y1uWMaPzrlO47cNfbcNd8+uvayaa9vXNAcXdgWF7bihWeLni36tvArQC8/chpZUx21Gon1k62hv9056W0Fkl2E2oOS/D9I4Fk2BdEICtcLu3Id34YF3V8GS7JuEATafKTdI2RCI+0+U6oFOtLKTUluFCQjyZNMwW0oAFj9ns868YxGalKoqMce07xwFdsnmnBBHzlTFQ1UrIGLxLwRXHoqssp1vHXp65Kjvi4wExYn9Vq8sFatgH3mbyo9fRq4SpgmQ6dEeNzxhj136PecgTs48YfHGyJ1hzVS+8XGRH+If7xohXvNoO73yr5FWD9o7Tk7VvLZ0e/36kJ9aDnE539G42dVf9ijvYSHmawfVlurIjT8yVIRkuU0oUTMX+fPK5KUdsIK8johuDNG4zcHBwi4fSoae1zf2qW1Gu/17WTGVFNkZKob2EEo+0TC+1jwjEXPN5qdTN3dt2+1QxtxngCpA9Gnhd14l/xsa28DVO6m+1x94QTC+xHPl3aj9TGGynoFXBmj8ZJ3xQrYfJbFAlqe59HeXWGbR3Btbx5X5hpN0t3Gj566i19YnX8HUEsHCGqraC7bBAAABCYAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAAFwAAAGdlb2dlYnJhX2RlZmF1bHRzM2QueG1s7ZjdbtMwFMev4Sks39PYaZIu0zJUwQVIMIF2w62XnLaGxA62uzZ7Nd6BZ+LEzroUNsSqbRKIXPT46xzHv79zEvfk5bapySUYK7UqKJ8wSkCVupJqWdC1W7w4oi9Pn58sQS/hwgiy0KYRrqBpP3Lnh7VJOjvq20TbFnRpRLvCEJS0tXC9T0E3lJCtlcdKn4kGbCtKOC9X0Ih3uhTOh1k51x5H0WazmVxPONFmGWFMG21tFS2XboKWErxrZQs6FI4x7p73Zur9YsZ49On9uzDPC6msE6oESnBFFSzEunYWi1BDA8oR17VQ0FIrWU5xjlpcQF3Qt8rhMqHsb5GUa3OJ/oNzQac8ZfT0+bMTu9Iboi8+47iCOrOGnb+vRP0Y7H6la22IKWjMKUHCnKG9QJvHiK5uV6KgbMJZuHiSM84zHgf/WnRgyKXAoCy0iLXTpQ/pWxeitnA9Fid/rysIPckwXsnGsybWAeqEk9sWoPKlsHzmNeu8/uN4UsG562ogbiXLLwos4k9HTn3hjawq6LdR8AG5BHWJRLSxqD3zs3TMD79iw27bcl/vuO+94qHZ++OtGrkl8+AxDwPncTDTYJJg0h0S+KrCfdr+F/ewBdP3nESDzL8ILrbSjvSe99XXexqz6UEaMy8x8wKzG3kfS0zcN48r509kW2HwQUaJSpwjlAFX/f3b73H7R6gUxoGVQo3Av+o7fiaf/Q3kH5P73SAxvoIRvw++vscPE+BB/PLcA4x57hF6u8tO6UNhLLU2lSXbgp6JM0wBg70a7CZYP3Qh+jfSMNud+fE2uOxAuLruVlAZrW74jppuEE8HxIc8UQ/60kgGKGmesSRLHkylQzf7vdjOTbmSDVQg9uGitE8HN9BNZh5ub/4Nth86zM2y2uf6lJs2JJM8cI3ZP8PVSNvsU+VPSDULKTpQzbO/kqoCt1vnWV8e59X0f169H82va1H5r7FhsR+v62Oq/MDjyt3JMUvy/pplPD3iScwfCtBjHDluPXD0jeFU0QVzFe8C3vcMQuZZMLNgjoLJ7zyfyKatZSnd76W1a7PAA/Ntn81D177KyWEqo9+tH86T2Z9u+5vAT3Ro4X/6fReNTvzR9d8Lpz8AUEsHCBnmYOpCAwAAAREAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAAFgAAAGdlb2dlYnJhX2phdmFzY3JpcHQuanNLK81LLsnMz1NIT0/yz/PMyyzR0FSorgUAUEsHCNY3vbkZAAAAFwAAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAADAAAAGdlb2dlYnJhLnhtbL1YW2/bNhR+bn/FgZ42IIlJSpTkwu6QpBs2oO2KZRuGPQygJdrmIkuCRMdO0R+/c0hJlnMpmqZYGpUieXgu37lRmf2w3xRwo5vWVOU84GcsAF1mVW7K1TzY2uVpGvzw+uVspauVXjQKllWzUXYeSKIczuHsTCYpram6ngerRtVrZBFAXShLZ+bBLgCTz4M3l2nEfpLhqWTTi9PoMr08PX8j35zKVFywy+TyR8HiAGDfmldl9V5tdFurTF9la71Rb6tMWSdwbW39ajLZ7XZnvWpnVbOaoPR2sm/zyWq1OMMxALSvbOdB9/IK+R6d3oXunGCMT/5699bLOTVla1WZ6QDI9q15/fLFbGfKvNrBzuR2jUhFpOZam9Ua0Uh4GsCEqGqEpNaZNTe6xbOjqbPeburAkamS9l/4NygGwwLIzY3JdTMP2BkLp6mYhkxM04RPk0QEUDVGl7Yj5p3QSc9udmP0zvOlNycyYtMEXWVasyj0PFiqokW7TLlsENxh3trbQi8UirXNFucHjfiJ+4ck5qMmduhkjwXuMXZCT4KPlMyrM5ItOapsq6pwnBl8Ag6S4QN8CicQJ7gigEuIcCXFlQRCWpM8ghCIhIcQRThGtMxj3KFt/B/FAee4A4KBECA4iBCnUoJEsoTOCqSNp44fw4eoUSN8QloLQ3zcWhjhI+gNGUnPBvWQYezeJFEjfynIArcYphBNURAtyIRDiDrgPGGAHENiz50dEQP65RARe5GASAH5oenEmYmnOKZbuOOZ3i/yIb/E+DiH3fFLdOwVdAJD205o4H4QfpX5KQv9IPwQ+UF6msifjDypN5RFniYKn2thb1/4FPvSkX2cjEB/kPZuCIH05k5/GqJuGvupCzTGWbea+tUpTeNnGhN+lTF8JNUn51OE9iJ5KJ8g83mBebAzfYqdz4T3QXAlFib6dc89keGT7LxXGb9CYnyUet/G4Cj9YvFcpP+7zIQ9WG38yLvx2zhi+uWOeG5lGoCQnxc5m/Q9edaBAO2aaLtUtnrTEixJAkkIsRh6ZEwtrGuUiYBEQhKP2uUJNcxYHnomdcz0qGfK9LhxxrSYuC6MfYp6nu+gIuqb6EnXRj/da6PY9aJD40MFiRUHwEYNMdXIrgOiFmLogUJSGxQxYJ+UAmKqw4+0Q7wpVq0ZsF3roh5QdzCast7aI+iyTd6/2gqpVeHugR19XmXXFwPYHSetWjtmizenwwXN36SO7m8vZoVa6AJvslcUCgA3qiD9nIRlVVroq2scOHburjjT26wwuVHln+j6/lr2frtZ6AbcazUwoeMwXCpdjR5fKh1NVlVNfnXbYqjA/m/d4Ok4kQHcdu+C6m2mKJCj6dl0/IM3v9tHttLYc9c3V9paNLEFtddtD+mqoSzpoKLJL+1FVRyW6sqU9lLVdtu4bwXUoSG9z8tVoR1azpF4n86uF9X+ysEkYs/r99saZ6cdBovVZVVUDWCeCYl2rbpx4UdHQ6oNVMzRMEfB/D5xHfb5VDgKNy786KjQk163zlTe28l6KaYFPz8KNRcFdDnflsa+7SfWZNcHS4ne+7jH8Jgl/xYsuyy50efI9iBmNrkTcrO2brTK27XWtg/Co1AbxVlnOx5YXuqiuBqTJffpWl1QflQlwPoqa6qi8I1s9J5VxXZTOgdDQyZ7T88m97SadUnb67ipcu2TLPQnjvZn17opdeFzosSY3Vbb1pP7qHQKblv9Qdn1eZn/pleo5wdFRd0iiJ704JtcZ2aDB7u0DjuPUQT/gV7xy7leNbp3ptfGh1CnJoyMGkDyKXsg67GzqsEMQaEOwCN1ZpPeuplV2JVcp9oYghGjeKP27laGRaDuiseszRpTU+bCAhvTtT4kZ25aYpGPcCHEWpTlXWeNpRjDz/WtXVeN++5UllaofBV6gx+ZYF2WltuNbkw2RKxyH7Co+ra37Yx3SUrxCtXiX4yPO2F+wBy3H8ljUEW9Vo4f8z88mjLOY95nr7qlAjrC03F/N8RMX1ML+oD22LEOOvSTWrQYl1ZjoGpdHv6W4BXtAl5Q30b6GIdb/JDAc0uzH0GLaJmPGHyD61yWnvvAGBt6qDV2jVmNH+hUcOgu5GDtXn42ea7LQXU1xAZ2Ie2rxkBfIwCu1o7S3ruKnLbHMGzpzzE95kvsd3vqot/tv4c5qH9w9F3v2MHLbemCIjgc/Lwz+2Z6Qx+S95waxb72Cl/B5cixn3Xjr8tlqy1hLzz2p2L6oJe7aHBuuZvRD4IuH8Ucqlplxt6SzOguopNxxrjm3v2l6fV/UEsHCJxE9uqtBgAANhMAAFBLAQIUABQACAgIAFFgl1Bqq2gu2wQAAAQmAAAXAAAAAAAAAAAAAAAAAAAAAABnZW9nZWJyYV9kZWZhdWx0czJkLnhtbFBLAQIUABQACAgIAFFgl1AZ5mDqQgMAAAERAAAXAAAAAAAAAAAAAAAAACAFAABnZW9nZWJyYV9kZWZhdWx0czNkLnhtbFBLAQIUABQACAgIAFFgl1DWN725GQAAABcAAAAWAAAAAAAAAAAAAAAAAKcIAABnZW9nZWJyYV9qYXZhc2NyaXB0LmpzUEsBAhQAFAAICAgAUWCXUJxE9uqtBgAANhMAAAwAAAAAAAAAAAAAAAAABAkAAGdlb2dlYnJhLnhtbFBLBQYAAAAABAAEAAgBAADrDwAAAAA=",
-};
-// is3D=is 3D applet using 3D view, AV=Algebra View, SV=Spreadsheet View, CV=CAS View, EV2=Graphics View 2, CP=Construction Protocol, PC=Probability Calculator DA=Data Analysis, FI=Function Inspector, macro=Macros
-var views = {'is3D': 0,'AV': 1,'SV': 0,'CV': 0,'EV2': 0,'CP': 0,'PC': 0,'DA': 0,'FI': 0,'macro': 0};
-var applet = new GGBApplet(exp1, '5.0', views);
-window.onload = function() {applet.inject('exp1')};
-applet.setPreviewImage('data:image/gif;base64,R0lGODlhAQABAAAAADs=','https://www.geogebra.org/images/GeoGebra_loading.png','https://www.geogebra.org/images/applet_play.png');
-</script>
+```{r}
+library("ggplot2")
+eq = function(x){2^x}
+ggplot(data.frame(x=c(-3, 3)), aes(x=x)) + 
+  stat_function(fun=eq)
+```
 

### 2020-05-17 ms-a4-2_non-linear-relationships.rmd
Updated syllabus and started adding lesson 1

@@
   html_document:
-    code_folding: "hide"
+    toc: true
+    toc_float: true
 ---
@@
 # [Syllabus](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf) {.tabset .tabset-fade .tabset-pills}
+
+## Hide
 
@@
 * use an exponential model to solve problems
-  + graph and recognise an exponential function in the form $y=a^x$ and $y=a^{-x} (a>0)$ using technology
+  + graph and recognise an exponential function in the form $y=a^x$ and $y=a^{-x} (a>0)$ with and without technology
   + interpret the meaning of the intercepts of an exponential graph in a variety of contexts
-  + construct and analyse an exponential model to solve a practical growth or decay problem
-* construct and analyse a quadratic model to solve practical problems involving quadratic functions of expressions of the form $y=ax^2+bx+c$, for example, braking distance against speed
+  + construct and analyse an exponential model of the form $y=ka^x$ and $y=ka^{-x} (a>0)$ where $k$ is a constant, to solve a practical growth or decay problem
+* construct and analyse a quadratic model to solve practical problems involving quadratic functions or expressions of the form $y=ax^2+bx+c$, for example, braking distance against speed
   + recognise the shape of a parabola and that it always has a turning point and an axis of symmetry
@@
   + interpret the turning point and intercepts of a parabola in a practical context
-  + consider the range of values for $x$ and $y$ for which the quadratic model makes sense in ap ractical context
+  + consider the range of values for $x$ and $y$ for which the quadratic model makes sense in a practical context
 * recognise that reciprocal functions of the form $y=\frac{k}{x}$, where $k$ is a constant, represent inverse variation, identify the rectangular hyperbolic shape of these graphs and their important features
@@
 
+# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
 ## Hide
 
-#  {.tabset .tabset-fade .tabset-pills}
+## Show
 
-## Exponentials {.tabset .tabset-fade .tabset-pills}
+### Introduction
 
-### Functions
+::: {.definition}
+Exponential functions are functions that have the $x$ as the power of the constant.
 
-```{r}
-library("ggplot2")
-eq = function(x){2^x}
-ggplot(data.frame(x=c(-3, 3)), aes(x=x)) + 
-  stat_function(fun=eq)
-```
+i.e. $$y=ka^x$$ Where $a$ and $k$ are constants.
+:::
 
-### Modelling
+For example, $$y=3\times2^x$$
 
-## Quadratics {.tabset .tabset-fade .tabset-pills}
+::: {.note}
+Note that the index operation happens before the mulitplication so $y=3\times2^x\neq6^x$
+:::
 
-### Functions
+### Graphs - Still sorting it out {.tabset .tabset-fade .tabset-pills}
 
-### Modelling
+#### $y=2^x$
 
-## Reciprocals {.tabset .tabset-fade .tabset-pills}
+#### $y=a^x$
 
-### Functions
+#### $y=a^{-x}$
 
-### Modelling
+#### $y=a^x$ and $y=a^{-x}$
 
-## Inverse variation
+#### $y=ka^x$
 
-## Miscellaneous problems
+### Observations
+
+* The graph is above the $x$-axis.
+  + $y$ can never be 0 or negative, unless $k<0$.
+* The graph always passes through the point $(0, k)$. $(k\times a^0=k\times1=k)$
+* Increasing the value of $a$ increases the steepness of the curve.
+* Increasing the value of $x$ by 1 magnifies the value of $y$ by a factor of $a$
+* The $x$-axis is an _asymptote_.
+  + The curve never touches the $x$-axis.
+* $a^x$ and $a^{-x}$ are reflections in the $y$-axis.
+* $y=a^{-x}$ has the same graph as $y=\left(\dfrac{1}{a}\right)^x$
+* $k$ stretches the graph vertically.
+
+### Sketching
+
+When sketching exponential graphs:
+
+1. Construct a table of values
+2. Draw a number plane
+3. Plot at least 4 points
+4. Draw a curve that goes through the points
+
+### Examples {.tabset .tabset-fade .tabset-pills}
+
+#### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+##### Question
+
+Draw the graph of $y=3^x$
+
+##### Show Solution
+
+Embed
+
+#### Example 2 {.tabset .tabset-fade .tabset-pills}
+
+##### Question
+
+Draw the graph of $y=3^{-x}$
+
+##### Show Solution
+
+Embed
+
+# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+# Quadratic Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_d_quadratic-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+# Reciprocal Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_e_reciprocal-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+# Reciprocal Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_f_reciprocal-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+# Inverse Variation [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_g_inverse-variation.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+# Miscellaneous Problems [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_h_miscellaneous-problems.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show

### 2021-01-19 ms-a1_formulae-and-equations.rmd
Update style.css to match latex templates, added ms-a1, removed additional pages from html

---
title: "MS-A1 Formulae and Equations"
output:
  html_document:
    toc: true
    toc_float: true
---

# [Syllabus](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf) {.tabset .tabset-fade .tabset-pills}

## Hide

## Show

::: {.syllabus}

Students:

* review substitution of numerical values into linear and non-linear algebraic expressions and equations
  + review evaluating the subject of a formula, given the value of other pronumerals in the formula
  + change the subject of a formula
  + solve problems involving formulae, including calculating distance, speed and time (with change of units of measurement as required) or calculating stopping distances of vehicles using a suitable formula
* develop and solve linear equations, including those derived from substituting values into a formula, or those developed from a word description
* calculate and interpret blood alcohol content (BAC) based on drink consumption and body weight
  + use formulae, both in word form and algebraic form, to calculate an estimate for blood alcohol content $(BAC)$, including $BAC_{Male}=\frac{10N-7.5H}{6.8M}$ and $BAC_{Female}=\frac{10N-7.5H}{5.5M}$ where $N$ is the number of standard drinks consumed, $H$ is the number of hours of drinking, and $M$ is the person's weight in kilograms.
  + determine the number of hours required for a person to stop consuming alcohol in order to reach zero BAC, eg using the formula $time=\frac{BAC}{0.015}$
  + describe the limitations of methods estimating BAC
* calculate required medication dosages for children and adults from packets, given age or weight, using Fried’s, Young’s or Clark’s formula as appropriate
  + Fried's formula: Dosage for children 1-2 years $=\frac{\text{age (in months)}\ \times\ \text{adult dosage}}{150}$
  + Young's formula: Dosage for children 1-12 years $=\frac{\text{age of child (in years)}\ \times\ \text{adult dosage}}{\text{age od child (in years)}\ +\ 150}$
  + Clark's formula: Dosage $=\frac{\text{weight in kg}\ \times\ \text{adult dosage}}{70}$
:::

# Substitution [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/a_substitution.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}

## Hide

## Show

::: {.syllabus}

**Syllabus**

* review substitution of numerical values into linear and non-linear algebraic expressions and equaitons

:::

### Why algebra?

**Algebra** is used Mathematicians to communicate mathematical ideas in a convenient way. **Variables** (letters and symbols) are used to represent unknown quantities whose value can change depending on the situation.

### Expressions

We can think of expressions as number crunching machines. Numbers are put in and then a related number is produced.

For example the expression $a^2+1$ starts with an input $a$, squares it and adds 1.

If the number -5 is fed into the machine, the machine **substitutes** the number 5 in place of a and then **evaluates** the result:

$$\begin{aligned}&a^2+1\\=\ &(\color{red}{-5})^2+1\\=\ &25+1\\ =\ &26\end{aligned}$$

::: {.important}

**Important Note**

To avoid making mistakes it is good practice to **always** substitute into brackets.

:::

### Examples {.tabset .tabset-fade .tabset-pills}

#### Example 1 {.tabset .tabset-fade .tabset-pills}

##### Question

::: {.example}

Evaluate the following, given $x=4$

a) $\quad2x-3$
b) $\quad\sqrt{6x+12}$

:::

##### Show Solution (a)

Evaluate the following, given $x=4$

a) $\quad2x-3$
b) $\quad\sqrt{6x+12}$

::: {.solution}

$\begin{aligned}&2x-3\\=\ &2(\color{red}{4})-3\\=\ &8-3\\=\ &5\end{aligned}$

:::

##### Show Solution (b)

Evaluate the following, given $x=4$

a) $\quad2x-3$
b) $\quad\sqrt{6x+12}$

::: {.solution}

$\begin{aligned}&\sqrt{6x+12}\\=\ &\sqrt{6(\color{red}{4})+12}\\=\ &\sqrt{24+12}\\=\ &\sqrt{36}\\=\ &6\end{aligned}$

:::

#### Example 2 {.tabset .tabset-fade .tabset-pills}

##### Question

::: {.example}

Evaluate $\quad a^2-5b+c\quad$ given $a=3$, $b=-3$, $c=7$

:::

##### Show Solution

Evaluate $\quad a^2-5b+c\quad$ given $a=3$, $b=-3$, $c=7$

::: {.solution}

$\begin{aligned}&a^2-5b+c\\=\ &(\color{red}{3})^2-5(\color{red}{-3})+(\color{red}{7})\\=\ &9+15+7\\=\ &31\end{aligned}$

:::

### 2021-01-19 ms-a4-2_non-linear-relationships.rmd
Update style.css to match latex templates, added ms-a1, removed additional pages from html

@@
 
-# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
 
@@
 
-# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
 
@@
 
-## Show
-
-# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
 
 ## Hide
-
-## Show
-
-# Quadratic Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_d_quadratic-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
-
-## Show
-
-# Reciprocal Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_e_reciprocal-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
-
-## Show
-
-# Reciprocal Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_f_reciprocal-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
-
-## Show
-
-# Inverse Variation [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_g_inverse-variation.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
-
-## Show
-
-# Miscellaneous Problems [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2_h_miscellaneous-problems.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
-
-## Show

### 2021-01-20 ms-a1_formulae-and-equations.rmd
Changed icons and theme.

@@
 
-# [Syllabus](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf) {.tabset .tabset-fade .tabset-pills}
+# Syllabus [![](open.svg){width=16}](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
 
@@
   + Clark's formula: Dosage $=\frac{\text{weight in kg}\ \times\ \text{adult dosage}}{70}$
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
 :::
 
-# Substitution [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/a_substitution.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Substitution [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/a_substitution.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
 

### 2021-01-20 ms-a4-2_non-linear-relationships.rmd
Changed icons and theme.

@@
 
-# Exponential Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Exponential Functions [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/a_exponential-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
 
@@
 
-# Exponential Models [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Exponential Models [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/b_exponential-models.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
 
@@
 
-# Quadratic Functions [![](pres.png)](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
+# Quadratic Functions [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A4.2/c_quadratic-functions.html){target="blank"} {.tabset .tabset-fade .tabset-pills}
 

### 2021-01-21 ms-a1_formulae-and-equations.rmd
Changed example formatting, added MS-A1_b

@@
 
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
 :::
@@
 
-### Examples {.tabset .tabset-fade .tabset-pills}
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
 
-#### Example 1 {.tabset .tabset-fade .tabset-pills}
+##### Hide
 
-##### Question
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
 
@@
 
-##### Show Solution (a)
+###### Solution (a)
 
@@
 
-##### Show Solution (b)
+###### Solution (b)
 
@@
 
-#### Example 2 {.tabset .tabset-fade .tabset-pills}
+##### Example 2 {.tabset .tabset-fade .tabset-pills}
 
-##### Question
+###### Question
 
@@
 
-##### Show Solution
+###### Solution
 
@@
 :::
+
+## Practice {.tabset .tabset-fade .tabset-pills}
+
+### Questions
+
+If $a=4$, $b=-1$, and $c=-3$, evaluate:
+
+a) $\quad3a$
+b) $\quad2a-3b$
+c) $\quad2ac$
+d) $\quad ac-3c$
+e) $\quad\dfrac{a}{2b}$
+f) $\quad\dfrac{2ac}{b-c}$
+g) $\quad(2c)^2$
+h) $\quad2c^2$
+
+### Answers
+
+a) $\quad12$
+b) $\quad11$
+c) $\quad-24$
+d) $\quad-3$
+e) $\quad-2$
+f) $\quad-12$
+g) $\quad36$
+h) $\quad18$
+
+# Solving Equations [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/b_solving-equations.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Hide
+
+## Show
+
+::: {.syllabus}
+
+**Syllabus**
+
+* develop and solve linear equations, including those derived from substituting values into a formula, or those developed from a word description
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
+:::
+
+### Equations
+
+::: {.definition}
+
+**Definition 1 - Equation**
+
+A statement asserting that two *expressions* are equal.
+
+:::
+
+For example:
+
+$$\underset{\overset{\uparrow}{\text{expression 1}}}{3n-3}\overset{\underset{\downarrow}{\text{is equal to}}}{=}\underset{\overset{\uparrow}{\text{expression 2}}}{n+1}$$
+
+### Solving Equations
+
+::: {.definition}
+
+**Definition 2**
+
+To **solve** an equation means to find the value of the unknown.
+
+:::
+
+In order to solve an equation we need to rearrange the equation to **isolate** the unknown.
+We do this by unpacking the equation using **inverse operations**.
+The inverse operations are performed on *both sides* of the equation to **maintain the balance**.
+
+Once you have found a solution, you can check it is correct by **substituting** back into the original equation.
+
+#### {.tabset .tabset-fade .tabset-pills}
+
+##### Hide
+
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Solve for $x$:
+
+a) $\quad2x-3=5$
+b) $\quad8=4x=-2$
+c) $\quad\dfrac{x}{4}+7=5$
+d) $\quad\dfrac{1}{3}(x+2)=6$
+
+:::
+
+###### Solution (a)
+
+Solve for $x$:
+
+a) $\quad2x-3=5$
+b) $\quad8=4x=-2$
+c) $\quad\dfrac{x}{4}+7=5$
+d) $\quad\dfrac{1}{3}(x+2)=6$
+
+::: {.solution}
+
+$\begin{aligned}2x-3&=5\\2x-3\color{red}{+3}&=5\color{red}{+3}\\2x&=8\\2x\color{red}{\div2}&=8\color{red}{\div2}\\x&=4\end{aligned}$
+
+:::
+
+###### Solution (b)
+
+Solve for $x$:
+
+a) $\quad2x-3=5$
+b) $\quad8=4x=-2$
+c) $\quad\dfrac{x}{4}+7=5$
+d) $\quad\dfrac{1}{3}(x+2)=6$
+
+::: {.solution}
+
+$\begin{aligned}8-4x&=-2\\8-4x\color{red}{+4x+2}&=-2\color{red}{+4x+2}\\10&=4x\\10\color{red}{\div4}&=4x\color{red}{\div4}\\\frac{10}{4}&=x\\x&=\frac{10}{4}\\x&=\frac{5}{2}=2.5\end{aligned}$
+
+:::
+
+::: {.note}
+
+It is best practice to have the unknown on the left hand side (LHS) in your answer.
+
+:::
+
+###### Solution (c)
+
+Solve for $x$:
+
+a) $\quad2x-3=5$
+b) $\quad8=4x=-2$
+c) $\quad\dfrac{x}{4}+7=5$
+d) $\quad\dfrac{1}{3}(x+2)=6$
+
+::: {.solution}
+
+$\begin{aligned}\frac{x}{4}+7&=5\\\frac{x}{4}+7\color{red}{-7}&=5\color{red}{-7}\\\frac{x}{4}&=-2\\\frac{x}{4}\color{red}{\times4}&=-2\color{red}{\times4}\\x&=-8\end{aligned}$
+
+:::
+
+###### Solution (d)
+
+Solve for $x$:
+
+a) $\quad2x-3=5$
+b) $\quad8=4x=-2$
+c) $\quad\dfrac{x}{4}+7=5$
+d) $\quad\dfrac{1}{3}(x+2)=6$
+
+::: {.solution}
+
+$\begin{aligned}\frac{1}{3}(x+2)&=6\\\frac{1}{3}(x+2)\color{red}{\times3}&=6\color{red}{\times3}\\x+2&=18\\x+2\color{red}{-2}&=18\color{red}{-2}\\x&=16\end{aligned}$
+
+:::
+
+### Repeated Unknowns
+
+If the unknown appears in the equation more than once, we follow these steps:
+1. Expand brackets and collect like terms.
+2. If the unknown appears on both sides of the equation, remove it from one side using inverse operations.
+3. Isolate the unknown and solve the equation.
+
+#### {.tabset .tabset-fade .tabset-pills}
+
+##### Hide
+
+##### Example 2 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Solve $\quad4(2x+5)-3(x-2)=16\quad$ for $x$.
+
+:::
+
+###### Solution
+
+Solve $\quad4(2x+5)-3(x-2)=16\quad$ for $x$.
+
+::: {.solution}
+
+$\begin{aligned}4(2x+5)-3(x-2)&=16\\8x+20-3x+6&=16\\5x+26&=16\\5x+26\color{red}{-26}&=16\color{red}{-26}\\5x&=-10\\5x\color{red}{\div5}&=-10\color{red}{\div5}\\x&=-2\end{aligned}$
+
+:::
+
+##### Example 3 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Solve for $x$:
+
+a) $\quad4x-3=3x+7$
+b) $\quad5-3(-1+x)=x$
+
+:::
+
+###### Solution (a)
+
+Solve for $x$:
+
+a) $\quad4x-3=3x+7$
+b) $\quad5-3(-1+x)=x$
+
+::: {.solution}
+
+$\begin{aligned}4x-3&=3x+7\\4x\color{red}{-3x}-3\color{red}{+3}&=3x\color{red}{-3x}+7\color{red}{+3}\\x&=10\end{aligned}$
+
+:::
+
+###### Solution (b)
+
+Solve for $x$:
+
+a) $\quad4x-3=3x+7$
+b) $\quad5-3(-1+x)=x$
+
+::: {.solution}
+
+$\begin{aligned}5-3(-1+x)&=x\\5+3-3x&=x\\8-3x\color{red}{+3x}&=x\color{red}{+3x}\\8&=4x\\8\color{red}{\div4}&=4x\color{red}{\div4}\\2&=x\\x&=2\end{aligned}$
+
+:::
+
+### Fractions
+
+For equations involving fractions, first write all fractions with a **common denominator**.
+
+For example:
+
+* In $\dfrac{2x}{3}=\dfrac{x}{4}$ the lowest common denominator is $\ \ 12$.
+* In $\dfrac{3}{x}=\dfrac{5}{2x-1}$ the lowest common denominator is $\ \ x(2x-1)$.
+
+Once the fractions have common denominators you can **equate the numerators**
+
+#### {.tabset .tabset-fade .tabset-pills}
+
+##### Hide
+
+##### Example 4 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Solve $\quad\dfrac{2-x}{3}=\dfrac{x}{5}\quad$ for $x$.
+
+:::
+
+###### Solution
+
+Solve $\quad\dfrac{2-x}{3}=\dfrac{x}{5}\quad$ for $x$.
+
+::: {.solution}
+
+$\begin{aligned}\frac{2-x}{3}&=\frac{x}{5}\\\frac{2-x}{3}\color{red}{\times\frac{5}{5}}&=\frac{x}{5}\color{red}{\times\frac{3}{3}}\\\frac{5(2-x)}{15}&=\frac{3x}{15}\\5(2-x)&=3x&\text{(equating the numerators)}\\10-5x&=3x\\10-5x\color{red}{+5x}&=3x\color{red}{+5x}\\10&=8x\\10\color{red}{\div8}&=8x\color{red}{\div8}\\\frac{10}{8}&=x\\x&=\frac{10}{8}\\x&=\frac{5}{4}=1.25\end{aligned}$
+
+:::
+
+##### Example 5 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Solve $\quad\dfrac{7}{x+1}=\dfrac{3}{x}\quad$ for $x$.
+
+:::
+
+###### Solution
+
+Solve $\quad\dfrac{7}{x+1}=\dfrac{3}{x}\quad$ for $x$.
+
+::: {.solution}
+
+$\begin{aligned}\frac{7}{x+1}&=\frac{3}{x}\\\frac{7}{x+1}\color{red}{\times\frac{x}{x}}&=\frac{3}{x}\color{red}{\times\frac{x+1}{x+1}}\\\frac{7x}{x(x+1)}&=\frac{3(x+1)}{x(x+1)}\\7x&=3(x+1)&\text{(equating the numerators)}\\7x&=3x+3\\7x\color{red}{-3x}&=3x\color{red}{-3x}+3\\4x&=3\\4x\color{red}{\div4}&=3\color{red}{\div4}\\x&=\frac{3}{4}=0.75\\\end{aligned}$
+
+:::

### 2021-01-21 ms-a1_formulae-and-equations.rmd
Added MS-A1_c and MS-A1_d

@@
 # Syllabus [![](open.svg){width=16}](https://syllabus.nesa.nsw.edu.au/assets/mathematics_standard/mathematics-standard-stage-6-syllabus-2017.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
 
@@
 
+## Hide
+
 # Substitution [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/a_substitution.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
 
@@
 #### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
-
-##### Hide
 
@@
 
+##### Hide
+
 ## Practice {.tabset .tabset-fade .tabset-pills}
@@
 
+## Hide
+
 # Solving Equations [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/b_solving-equations.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
-
-## Hide
 
@@
 #### {.tabset .tabset-fade .tabset-pills}
-
-##### Hide
 
@@
 
+##### Hide
+
 ### Repeated Unknowns
@@
 
+##### Hide
+
 ### Fractions
@@
 
-* In $\dfrac{2x}{3}=\dfrac{x}{4}$ the lowest common denominator is $\ \ 12$.
-* In $\dfrac{3}{x}=\dfrac{5}{2x-1}$ the lowest common denominator is $\ \ x(2x-1)$.
+* In $\ \ \dfrac{2x}{3}=\dfrac{x}{4}\ \ $ the (lowest) common denominator is $\ \ 12$.
+* In $\ \ \dfrac{3}{x}=\dfrac{5}{2x-1}\ \ $ the common denominator is $\ \ x(2x-1)$.
 
@@
 :::
+
+##### Hide
+
+## Hide
+
+# Formulae [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/c_formulae.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Show
+
+::: {.syllabus}
+
+**Syllabus**
+
+* review evaluating the subject of a formula, given the value of other pronumerals in the formula
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
+:::
+
+### Formulae
+
+::: {.definition}
+
+A **formula** is an equation which connects two or more variables. The plural of formula is **formulae** or **formulas**.
+
+:::
+
+Generally a formula is written with a single variable, the **subject** on the LHS and the rest on the right.
+
+$$\underset{\overset{\uparrow}{\text{subject}}}{A}=\frac{1}{2}ab\cos{C}$$
+
+### Formula substitution
+
+If the formula contains two or more variables and we know the value of all but one of them, we can solve an equation to find the remaining variable.
+
+1) State the variables in the formula and the known values.
+2) Write down the formula and Substitute the known values into the formula.
+3) Solve the one variable equation to find the unknown value.
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+The area of a trapezium is given by $\ \ A=\dfrac{h}{2}(a+b)\ \ $ where $a$ and $b$ are the lengths of the parallel sides and $h$ is the height.
+
+Calculate the height of a 20 cm$^2$ trapezium with parallel lengths of 3 cm and 7 cm.
+
+:::
+
+###### Solution
+
+The area of a trapezium is given by $\ \ A=\dfrac{h}{2}(a+b)\ \ $ where $a$ and $b$ are the lengths of the parallel sides and $h$ is the height.
+
+Calculate the height of a 20 cm$^2$ trapezium with parallel lengths of 3 cm and 7 cm.
+
+::: {.solution}
+
+<div class="row">
+  <div class="column">
+  $\begin{aligned}A&=20\text{ cm}^2\\h&=\ ?\\a&=3\text{ cm}^2\\b&=7\text{ cm}^2\end{aligned}$
+  </div>
+  <div class="column">
+  $\begin{aligned}A&=\frac{h}{2}(a+b)\\20&=\frac{h}{2}(3+7)\\20&=\frac{h}{2}(10)\\20&=5h\\20\color{red}{\div5}&=5h\color{red}{\div5}\\4&=h\\h&=4\text{ cm}\end{aligned}$
+  </div>
+</div>
+
+The height of the trapezium is equal to 4 cm.
+
+:::
+
+##### Hide
+
+## Hide
+# Rearranging Formulae [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/d_rearranging-formulae.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Show
+
+::: {.syllabus}
+
+**Syllabus**
+
+* change the subject of a formula
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
+:::
+
+### Formula Rearrangement
+
+By performing operations to both sides of a formula, they can be **rearranged** to make **equivalent** formulae where other variables are the subjects.
+
+<div class="row">
+  <div class="column">
+  $$\begin{aligned}V&=\pi r^2h\\V\color{red}{\div\pi r^2}&=\pi r^2h\color{red}{\div\pi r^2}\\\frac{V}{\pi r^2}&=h\\h&=\frac{V}{\pi r^2}\end{aligned}$$
+  </div>
+  <div class="column">
+  $$\begin{aligned}V&=\pi r^2h\\V\color{red}{\div\pi h}&=\pi r^2h\color{red}{\div\pi h}\\\frac{V}{\pi h}&=r^2\\r^2&=\frac{V}{\pi h}\\\color{red}{\sqrt{\color{black}{r^2}}}&=\color{red}{\sqrt{\color{black}{\frac{V}{\pi h}}}}\\r&=\sqrt{\frac{V}{\pi h}}&(r>0)\end{aligned}$$
+  </div>
+</div>
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Make $a$ the subject of $\quad2a-7b=23$.
+
+:::
+
+###### Solution
+
+Make $a$ the subject of $\quad2a-7b=23$.
+
+::: {.solution}
+
+$\begin{aligned}2a-7b&=23\\2a-7b\color{red}{+7b}&=23\color{red}{+7b}\\2a&=23-7b\\\color{red}{\frac{\color{black}{2a}}{2}}&=\color{red}{\frac{\color{black}{23-7b}}{2}}\\a&=\frac{23-7b}{2}\end{aligned}$
+
+:::
+
+##### Hide
+
+### Rearranging and substituting
+
+Previously, during formula substitution, the variables were replaced by numbers and then the equation was solved.
+However, often we need to substitute several values for the unknowns and solve the equation for each case.
+In this situation it is quicker to **rearrange** the formula **before substituting**.
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 2 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+The surface area of a sphere is given by $\ \ A=4\pi r^2\ \ $ where $r$ is the sphere's radius.
+
+a) Rearrange this formula to make $r$ the subject.
+b) Hence find the radius to 3 significant figures when the surface area is:
+    i) 10 cm$^2$
+    ii) 20 cm$^2$
+    iii) 30 cm$^3$
+
+:::
+
+###### Solution (a)
+
+The surface area of a sphere is given by $\ \ A=4\pi r^2\ \ $ where $r$ is the sphere's radius.
+
+a) Rearrange this formula to make $r$ the subject.
+b) Hence find the radius to 3 significant figures when the surface area is:
+    i) 10 cm$^2$
+    ii) 20 cm$^2$
+    iii) 30 cm$^3$
+
+::: {.solution}
+
+$\begin{aligned}A&=4\pi r^2\\A\color{red}{\div4\pi}&=4\pi r^2\color{red}{\div4\pi}\\\frac{A}{4\pi}&=r^2\\\color{red}{\sqrt{\color{black}{\frac{A}{4\pi}}}}&=\color{red}{\sqrt{\color{black}{r^2}}}\\r&=\sqrt{\frac{A}{4\pi}}&(r>0)\end{aligned}$
+
+:::
+
+###### Solution (b)
+
+The surface area of a sphere is given by $\ \ A=4\pi r^2\ \ $ where $r$ is the sphere's radius.
+
+a) Rearrange this formula to make $r$ the subject.
+b) Hence find the radius to 3 significant figures when the surface area is:
+    i) 10 cm$^2$
+    ii) 20 cm$^2$
+    iii) 30 cm$^3$
+
+::: {.solution}
+
+$\begin{aligned}\text{i) }\ \ r&=\sqrt{\frac{A}{4\pi}}&\text{ii) }\ \ r&=\sqrt{\frac{A}{4\pi}}&\text{iii) }\ \ r&=\sqrt{\frac{A}{4\pi}}\\\\r&=\sqrt{\frac{\color{red}{10}}{4\pi}}&r&=\sqrt{\frac{\color{red}{20}}{4\pi}}&r&=\sqrt{\frac{\color{red}{30}}{4\pi}}\\\\r&=0.892\text{ cm}&r&=1.26\text{ cm}&r&=1.55\text{ cm}\end{aligned}$
+
+:::
+
+##### Hide
+
+## Hide

### 2021-01-26 ms-a1_formulae-and-equations.rmd
Added MS-A1_e, MS-A1_f and MS-A1_g. Added calc font, added formula box

@@
   + Fried's formula: Dosage for children 1-2 years $=\frac{\text{age (in months)}\ \times\ \text{adult dosage}}{150}$
-  + Young's formula: Dosage for children 1-12 years $=\frac{\text{age of child (in years)}\ \times\ \text{adult dosage}}{\text{age od child (in years)}\ +\ 150}$
+  + Young's formula: Dosage for children 1-12 years $=\frac{\text{age of child (in years)}\ \times\ \text{adult dosage}}{\text{age of child (in years)}\ +\ 150}$
   + Clark's formula: Dosage $=\frac{\text{weight in kg}\ \times\ \text{adult dosage}}{70}$
@@
 ## Hide
+
+# Speed, Distance and Time [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/e_speed-distance-time.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Show
+
+::: {.syllabus}
+
+**Syllabus**
+
+* review substitution of numerical values into linear and non-linear algebraic expressions and equations
+  + solve problems involving formulae, including calculating distance, speed and time (with change of units of measurement as required) or calculating stopping distances of vehicles using a suitable formula
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
+:::
+
+### Speed
+
+::: {.definition}
+
+**Definition**
+
+**Speed** is a comparison between *distance travelled* and *time taken*
+
+:::
+
+In most real world situations, an objects speed is not constant. Therefore we often use the **average speed**.
+
+::: {.formula}
+
+$$s=\frac{d}{t}$$
+
+Where:
+
+* $s$ - average speed
+* $d$ - distance travelled
+* $t$ - time taken
+
+::: {.important}
+
+The formula is **not** on the reference sheet.
+
+:::
+
+:::
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Find the average speed of a car which travels 110 km in 2 hours.
+
+:::
+
+###### Solution
+
+Find the average speed of a car which travels 110 km in 2 hours
+
+::: {.solution}
+
+$\begin{aligned}s&=\frac{d}{t}\\&=\frac{110\text{ km}}{2\text{ h}}\\&= 55\text{ km/h}\end{aligned}$
+
+:::
+
+##### Hide
+
+### Rearranging
+
+The formula for speed can be rewritten to make *distance* or *time* the subject.
+
+$$s=\frac{d}{t}$$
+
+$$d=st$$
+
+$$t=\frac{d}{s}$$
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 2 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Jonah rides his motorcycle on a highway at an average speed of 90 km/h.
+
+a) How far can Jonah travel in $1\frac{1}{2}$ hours?
+b) How long will he take to travel 210 km? Answer in hours and minutes.
+
+:::
+
+###### Solution (a)
+
+Jonah rides his motorcycle on a highway at an average speed of 90 km/h.
+
+a) How far can Jonah travel in $1\frac{1}{2}$ hours?
+b) How long will he take to travel 210 km? Answer in hours and minutes.
+
+::: {.solution}
+
+<div class="row">
+  <div class="column">
+  $\begin{aligned}d&=st\\d&=(90)\underset{\color{red}{(*)}}{\left(\color{red}{1\frac{1}{2}}\right)}\\d&=135\text{ km}\end{aligned}$
+  </div>
+  <div class="column">
+  $(*)=$ <span style="font-family: casio">qa1$1R2</span>
+  </div>
+</div>
+
+:::
+
+###### Solution (b)
+
+Jonah rides his motorcycle on a highway at an average speed of 90 km/h.
+
+a) How far can Jonah travel in $1\frac{1}{2}$ hours?
+b) How long will he take to travel 210 km? Answer in hours and minutes.
+
+::: {.solution}
+
+<div class="row">
+  <div class="column">
+  $\begin{aligned}t&=\frac{d}{s}\\t&=\frac{210}{90}\\t&=2.33...\text{ h}\\&\quad\color{red}{(*)}\\t&=2^\circ 20' 0''\end{aligned}$
+
+  2 hours and 20 minutes
+  </div>
+  <div class="column">
+  $(*)=$ <span style="font-family: casio">x</span>
+  </div>
+</div>
+
+:::
+
+##### Hide
+
+### Stopping distance
+
+::: {.definition}
+
+**Definition - Stopping distance**
+
+The distance a vehicle will travel in order to come to a complete stop.
+
+:::
+
+<center>stopping distance = reaction distance + braking distance</center>
+
+::: {.important}
+
+**Important Note**
+
+You **are not** expected to memorise any formulae.
+
+You **are** expected to be able to substitute into a given formula.
+
+:::
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 3 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Claire is driving on a motorway at a speed of 110 kilometres per hour and has to brake suddenly. She has a reaction time of 2 seconds and a braking distance of 59.2 metres.
+
+What is Claire's stopping distance?
+
+:::
+
+###### Solution
+
+Claire is driving on a motorway at a speed of 110 kilometres per hour and has to brake suddenly. She has a reaction time of 2 seconds and a braking distance of 59.2 metres.
+
+What is Claire's stopping distance?
+
+::: {.solution}
+
+$\begin{aligned}110\text{ km/h}&=110000\text{ m/hr}\\&=\frac{110000}{60\times60}\text{ m/s}\\&=30.555...\text{ m/s}\end{aligned}$
+
+Let $d$ be Claire's stopping distance.
+
+$\begin{aligned}d&=\underbrace{\text{reaction time distance}}_{d=st}+\text{braking distance}\\&=st+\text{braking distance}\\&=(30.555...)(2)+(59.2)\\&=120.311...\\d&=120.3 \text{ m (1 d.p.)}\end{aligned}$
+
+Claire's stopping distance is 120.3 metres.
+
+:::
+
+##### Example 4 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Max was driving 60 km/h and has a reaction time of 0.8 s.
+Calculate the stopping distance correct to the nearest metre given the formula $\quad d=\dfrac{5vt}{18}+\dfrac{v^2}{170}\quad$ where $d$ is the stopping distance (m), $v$ is the speed (m/s) and $t$ is reaction time (s).
+
+:::
+
+###### Solution
+
+Max was driving 60 km/h and has a reaction time of 0.8 s.
+Calculate the stopping distance correct to the nearest metre given the formula $\quad d=\dfrac{5vt}{18}+\dfrac{v^2}{170}\quad$ where $d$ is the stopping distance (m), $v$ is the speed (m/s) and $t$ is reaction time (s).
+
+::: {.solution}
+
+\begin{aligned}d&=\frac{5vt}{18}+\frac{v^2}{170}\\d&=\frac{5(60)(0.8)}{18}+\frac{60^2}{170}\\d&=34.509...\\d&\approx35\text{ m}\end{aligned}
+
+Max's stopping distance is 35 metres.
+
+:::
+
+##### Hide
+
+## Hide
+
+# Blood Alcohol Content [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/f_blood-alcohol-content.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Show
+
+::: {.syllabus}
+
+**Syllabus**
+
+* calculate and interpret blood alcohol content (BAC) based on drink consumption and body weight
+  + use formulae, both in word form and algebraic form, to calculate an estimate for blood alcohol content $(BAC)$, including $BAC_{Male}=\frac{10N-7.5H}{6.8M}$ and $BAC_{Female}=\frac{10N-7.5H}{5.5M}$ where $N$ is the number of standard drinks consumed, $H$ is the number of hours of drinking, and $M$ is the person's weight in kilograms.
+  + determine the number of hours required for a person to stop consuming alcohol in order to reach zero BAC, eg using the formula $time=\frac{BAC}{0.015}$
+  + describe the limitations of methods estimating BAC
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
+:::
+
+### Blood Alcohol Content
+
+::: {.definition}
+
+**Definition**
+
+Blood alcohol content (BAC) is a measure of the amount of alcohol in your blood.
+
+:::
+
+BAC tells you the number of grams of alcohol per 100 mL of blood
+
+For example, a BAC of 0.10 means there is 0.10 g of alcohol for every 100 mL of blood, or 1 g for every 1 L of blood.
+
+### Estimating BAC
+
+BAC can be estimated using the following formulae:
+
+::: {.formula}
+
+$$BAC_{\text{Male}}=\frac{10N-7.5H}{6.8M}\quad\text{or}\quad BAC_{\text{Female}}=\frac{10N-7.5H}{5.5M}$$
+
+Where:
+* $BAC$ - Blood alcohol content
+* $N$ - Number of standard drinks consumed
+* $H$ - Hours drinking
+* $M$ - Mass in kilograms
+
+::: {.important}
+
+These formulae are **not** on the reference sheet.
+
+You are **not** expected to remember these formulae.
+
+:::
+
+:::
+
+### Limitations
+
+These formulae are only good for calculating *estimates* of a person BAC.
+
+The formulae for estimating BAC only takes into account the number of standard drinks consumed, sex, the amount of time, and mass.
+
+There are other factors that influence BAC including:
+
+* Fitness
+* Health
+* Liver function
+* Food in the stomach
+* Medications
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Osman is 87 kg and has consumed 3 standard drinks in the past hour.
+Estimate Osman's BAC to 3 decimak places using the following formula where $N$ represents the number of standard drinks, $H$ is the number of hours drinking and $M$ is his mass in kilograms.
+
+$$BAC_{\text{Male}}=\frac{10N-7.5H}{6.8M}$$
+
+:::
+
+###### Solution
+
+Osman is 87 kg and has consumed 3 standard drinks in the past hour.
+Estimate Osman's BAC to 3 decimak places using the following formula where $N$ represents the number of standard drinks, $H$ is the number of hours drinking and $M$ is his mass in kilograms.
+
+$$BAC_{\text{Male}}=\frac{10N-7.5H}{6.8M}$$
+
+::: {.solution}
+
+$\begin{aligned}BAC_{\text{Male}}&=\frac{10N-7.5H}{6.8M}\\&=\frac{10(3)-7.5(1)}{6.8(87)}\\&=0.038032...\\&\approx0.038\end{aligned}$
+
+:::
+
+##### Hide
+
+### Reaching zero BAC
+
+The number of hours required for a person to reach zero BAC after they stop consuming alcohol is given by the following formula:
+
+::: {.formula}
+
+$$\text{Time (h)}=\frac{BAC}{0.015}$$
+
+::: {.important}
+
+This formula is **not** on the reference sheet.
+
+You are **not** expected to remember this formula.
+:::
+
+:::
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 2 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Fiona has a BAC of 0.027. Use the following formula to estimate the time she will need for her BAC to reach zero. Answer to the nearest minute.
+
+$$\text{Time}=\frac{BAC}{0.015}$$
+
+:::
+
+###### Solution
+
+Fiona has a BAC of 0.027. Use the following formula to estimate the time she will need for her BAC to reach zero. Answer to the nearest minute.
+
+$$\text{Time}=\frac{BAC}{0.015}$$
+
+::: {.solution}
+
+<div class="row">
+  <div class="column">
+  $\begin{aligned}\text{Time}&=\frac{BAC}{0.015}\\&=\frac{(0.027)}{0.015}\\&=1.8\\&\quad(*)\\&=1^\circ48'0''\end{aligned}$
+
+  Fiona needs to wait 1 hour and 48 minutes.
+  </div>
+  <div class="column">
+  $(*)=$ <span style="font-family: casio">x</span>
+  </div>
+</div>
+
+:::
+
+##### Hide
+
+## Hide
+
+# Medication [![](pres.svg){width=16}](https://claytonpollard.github.io/stage6_standard_presentations/MS-A1/g_medication.pdf){target="blank"} {.tabset .tabset-fade .tabset-pills}
+
+## Show
+
+::: {.syllabus}
+
+**Syllabus**
+
+* calculate required medication dosages for children and adults from packets, given age or weight, using Fried’s, Young’s or Clark’s formula as appropriate
+  + Fried's formula: Dosage for children 1-2 years $=\frac{\text{age (in months)}\ \times\ \text{adult dosage}}{150}$
+  + Young's formula: Dosage for children 1-12 years $=\frac{\text{age of child (in years)}\ \times\ \text{adult dosage}}{\text{age of child (in years)}\ +\ 150}$
+  + Clark's formula: Dosage $=\frac{\text{weight in kg}\ \times\ \text{adult dosage}}{70}$
+
+<div align="right"><i><small>As of 2021/01/20</small></i></div>
+:::
+
+### Converting concentrations
+
+A concentration is a rate comparing a mass (g, mg, etc.) with a volume (L, mL, etc.). We need to consider both when converting a concentration from one unit to another.
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 1 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+The concentration of a mild analgesic is given as 80 mg per 50 mL. What is in g/mL?
+
+:::
+
+###### Solution
+
+The concentration of a mild analgesic is given as 80 mg per 50 mL. What is in g/mL?
+
+::: {.solution}
+
+$\begin{aligned}80\text{ mg}/50\text{ mL}&=\frac{80\text{ mg}}{50\text{ mL}}\\&=1.6\text{ mg/mL}\\&=1.6\div1000\text{ g/mL}\\&=0.0016\text{ g/mL}\end{aligned}$
+
+:::
+
+##### Hide
+
+### Calculating dosages
+
+Often when calculating dosages you will be prescribed an amount in milligrams (mg) and need to calculate how much of a liquid that need to be taken. In these cases you can use the following:
+
+::: {.formula}
+
+$$\text{volume required}=\frac{\text{strength required}}{\text{strength of stock}}\times\text{volume of stock}$$
+
+Where your *stock* is the medication you're given.
+
+::: {.important}
+
+This formula is **not** on the reference sheet.
+
+:::
+
+:::
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 2 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+A patient is prescribed 1000 mg of a mild painkiller. The medication available contains 100 mg in 5 mL. How much medication should be given to the patient?
+
+:::
+
+###### Solution
+
+A patient is prescribed 1000 mg of a mild painkiller. The medication available contains 100 mg in 5 mL. How much medication should be given to the patient?
+
+::: {.solution}
+
+$\begin{aligned}\text{volume required}&=\frac{\text{strength required}}{\text{strength of stock}}\times\text{volume of stock}\\&=\frac{(1000\text{ mg})}{(100\text{ mg})}\times(5\text{ mL})\\&=50\text{ mL}\end{aligned}$
+
+:::
+
+##### Hide
+
+### Children and infants
+
+There are three formulae used for children and infants:
+
+::: {.formula}
+
+* Fried's formula: Dosage for children 1-2 years $=\dfrac{\text{age (months)}\ \times\ \text{adult dosage}}{150}$
+* Young's formula: Dosage for children 1-12 years $=\dfrac{\text{age of child (years)}\ \times\ \text{adult dosage}}{\text{age of child (years)}\ +\ 150}$
+* Clark's formula: Dosage $=\dfrac{\text{weight (kg)}\ \times\ \text{adult dosage}}{70}$
+
+::: {.important}
+
+These formulae are **not** on the reference sheet.
+
+You are **not** expected to remember these formulae.
+
+:::
+
+:::
+
+#### {.tabset .tabset-fade .tabset-pills .unlisted .unnumbered}
+
+##### Example 3 {.tabset .tabset-fade .tabset-pills}
+
+###### Question
+
+::: {.example}
+
+Jessica is 6 months old. Use Fried's formula to find the required infant dose if the adult dost is 20 mL.
+
+$$\text{Dosage}=\dfrac{\text{age (months)}\ \times\ \text{adult dosage}}{150}$$
+
+:::
+
+###### Solution
+
+Jessica is 6 months old. Use Fried's formula to find the required infant dose if the adult dost is 20 mL.
+
+$$\text{Dosage}=\dfrac{\text{age (months)}\ \times\ \text{adult dosage}}{150}$$
+
+::: {.solution}
+
+$\begin{aligned}\text{Dosage}&=\frac{\text{age (months)}\ \times\ \text{adult dosage}}{150}\\&=\frac{(6)\times(20)}{(150)}\\&=\frac{120}{150}\\&=0.8\text{ mL}\end{aligned}$
+
+:::
+
+##### Hide
+
+## Hide
